Exploring probability distributions for bivariate temporal granularities

### 2019-12-07 main.Rmd
aperiodic granularity done

Aperiodic cyclic granularities are defined using aperiodic linear granularities. Consider n aperiodic linear granularity $A_i$ such that $B \trianglelefteq A_i, \forall i\in{1, 2, \dots, n}$. Then according to \autoref{def:groupsinto}, for each index $j$ there exists a (possibly infinite) subset $T_{\{i, j\}}$ of the integers such
that
\begin{equation*}
A_(j) = \bigcup_{z \in T_{\{i, j\}}}B(z)
\end{equation*}

\begin{definition}\label{aperiodic}
An aperiodic granularity $AX_{B, G''}$ that relates linear granularities $G''$ and bottom granularity $B$, with $G''$ being aperiodical with respect to $B$, is given by

\begin{equation}\label{eq:eq7}
\begin{split}
A_{B, G''}(z) & = L(i) \quad z \in T_q(i) \quad and \quad \forall i \in E \\
     & = L(0) otherwise
\end{split}     
\end{equation}
where, 
$z$ denotes the index set,
$T_q$ are the sets of indices of $B$ describing $G''(q)$ such that $$G''(q) = \bigcup_{z \in T_q}B(z)$$ and $T_q(z) = \bigcup_{i \in E} T_q(i)$, E denotes the set of linear aperiodic granularities.
\end{definition}

Discussion: Aperiodic cyclic time granularities relate many aperiodic linear granularities to the bottom granularity. The number of categories obtained coincides with the number of aperiodic linear granularities considered.

map a time index to a categorical variable containing binary values. It takes the value 1 whenever the time index coincides with the events in context (e.g. public or school holiday) and 0 when it does not. Here, 1 and 0 are proxies to denote the binary categorization and can be replaced with a logical vector. An example of aperiodic granularity can be one that relates a bottom granularity ($B$) and linear granularity ($G''$) such that $BG \trianglelefteq G''$, $BG \not\preceq G$ and $B$ is not periodic or quasi-periodic with respect to $G''$, as shown in \autoref{fig:aperiodic}.

```{r aperiodic, echo=FALSE,out.width = "100%",fig.cap="Relating aperiodic granularity and bottom linear granularity "}
knitr::include_graphics("Figs/aperiodic.png")
```

>>>>

Aperiodic cyclic granularities are defined using aperiodic linear granularities. Consider n aperiodic linear granularities $M_i$  $\forall \{i\in{1, 2, \dots, n\}}$ none of which can be expressed as periodic or quasi-periodic with respect to the bottom granularity. Further assume that $B \trianglelefteq M_i$ $\forall \{i\in{1, 2, \dots, n\}}$. Then according to \autoref{def:groupsinto}, for each index $j$ there exists a (possibly infinite) subset $T_{\{i_j\}}$ of the integers such that
\begin{equation*}
M_{i}(j) = \bigcup_{z \in T_{i_j}}B(z)
\end{equation*}
and suppose $M = \bigcup_{i=1}^{n}M_{i}$ is formed by collecting the granules of $\{M_1, M_2, \dots, M_n\}$.

\begin{definition}\label{aperiodic}
An aperiodic cyclic granularity $A_{B, M}$ relates aperiodic linear granularity $M$ and bottom granularity $B$, if

\begin{equation}\label{eq:aperiodic}
\begin{split}
A_{B, M}(z) & = L(i), \quad z \in T_{i_j} \quad and \quad \forall i \in {1, 2, \dots, n}\\
     & = L(0), \quad otherwise
\end{split}     
\end{equation}
where, 
$z \in \mathbb{Z}_{\geq 0}$ denotes the index set,
$T_{i_j}$ are the sets of indices of $B$ describing $M_{i}(j)$ such that $M_{i}(j) = \bigcup_{z \in T_{i_j}}B(z)$ and $M = \bigcup_{j=1}^{n}M_{j}$.
\end{definition}

**Example**: \autoref{fig:aperiodic-example} shows two aperiodic linear granularity $M_1$ and $M_2$. Each granule is represented by a box. The diagram also illustrates that the granules that overlap share elements from the underlying time domain. The first slot in the diagram shows the index set and A_{B, M} consists of three categories, one corresponding to the first aperiodic event $M_1$, the second corresponding to aperiodic event $M_2$ and the third corresponding to no event/aperiodic linear granularity.

**Discussion**: The number of categories obtained coincides with the number of aperiodic linear granularities considered and an additional category representing no event. The index ${\{i_j\}}$ stands for the $j^{th}$ granule of the $i^{th}$ linear aperiodic granularity considered.

<!-- map a time index to a categorical variable containing binary values. It takes the value 1 whenever the time index coincides with the events in context (e.g. public or school holiday) and 0 when it does not. Here, 1 and 0 are proxies to denote the binary categorization and can be replaced with a logical vector. -->

```{r aperiodic-example, echo=FALSE,out.width = "100%",fig.cap="Relating aperiodic granularity and bottom linear granularity "}
knitr::include_graphics("Figs/aperiodic-example.png")
```
